**Kids Hobby Prediction Dataset**

Following the selection of our data set ("Hobby_Data"), we will begin to work and analyse the data in order to accomplish our goal. The data set will initially be ready. by acting The preprocessing procedures:

#1# Data cleaning

During the data cleaning stage, Finding and fixing faults, inconsistencies, and errors in a dataset helps it be more reliable and of higher quality for analysis and modelling. There are methods for handling missing values, detecting outliers, resolving inconsistencies, and standardising formats.

-   import Dataset"Hobby_Data"

```{r}
setwd("/Users/96653/Documents/GitHub/KidsHobby/Dataset")


dataset = read.csv('Hobby_Data.csv')

dataset = read.csv("Hobby_Data.csv")

View(dataset)

str(dataset)
```

**1- check missing value :**

```{r}
is.na(dataset)
```

-   **find the total null values in the dataset**

```{r}
sum(is.na(dataset))
```

We simply look for missing values and no missing values in their ,According to our investigation, the dataset does not contain any outliers , since numric Data Type is not included. also there are no inconsistent values,or other errors.
