**Kids Hobby Prediction Dataset**

Following the selection of our data set ("Hobby_Data"), we will begin to work and analyse the data in order to accomplish our aim. First, we will prepare the data set in the

preprocessing steps:

#1# Data cleaning

We perform a data cleaning process after reading a dataset in which we search for missing values and outliers. According to our investigation, the dataset does not contain any intentional errors or incorrect data values.

- import Dataset"Hobby_Data"
```{r}


setwd("/Users/96653/Documents/GitHub/KidsHobby/Dataset")


dataset = read.csv('Hobby_Data.csv')

View(dataset)

str(dataset)
```

**1- check missing value :**

```{r}
is.na(dataset)
```


-    find the total null values in the dataset
```{r}
sum(is.na(dataset))
```




**2-Detect Outliers**

-   Detect outlier in Time_sprt
```{r}
library(outliers)

OutTime_sprt = outlier(dataset$Time_sprt, logical =TRUE)

sum(OutTime_sprt)

Find_outlier = which(OutTime_sprt ==TRUE, arr.ind = TRUE)

OutTime_sprt

Find_outlier

```




-   Detect outlier in Grasp_pow
```{r}
OutGrasp_pow = outlier(dataset$Grasp_pow, logical =TRUE)

sum(OutGrasp_pow)

Find2_outlier = which(OutGrasp_pow ==TRUE, arr.ind = TRUE)

OutGrasp_pow

Find2_outlier
```



-   Detect outlier in Time_art
```{r}

OutTime_art= outlier(dataset$Time_art, logical =TRUE)

sum(OutTime_art)

Find3_outlier = which(OutTime_art ==TRUE, arr.ind = TRUE)

OutTime_art

Find3_outlier
```




**3-Removing Outliers**

-   removing outlier in Time_sprt
```{r}
dataset= dataset[-Find_outlier,]

print(dataset)
```



-   removing outlier in Grasp_pow
```{r}
dataset= dataset[-Find2_outlier,]

print(dataset)

```

d

-   removing outlie in Time_art
```{r}
dataset= dataset[-Find3_outlier,]

print(dataset)
```

